On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-05-12 Manuscript/manuscript.tex
Moved a paragraph commented out in the intro to the end of the data section

%4)
The objective to this paper is to analyze the reaction times at the 2022 World 
Track and Field Championships to check for any abnormalities, and we approach
this two different ways.  First we model the data, which is
the reaction times of every non-disqualification since the 1999 World 
Championships, using a gamma linear mixed-effects model with a random effect 
accounting for the venue (or year). 
%\eds{are you using covariates?  Data section
%implies that you are, but Results section does not}
%\of{Cleaned up confusion about covariates, but no none were used in the paper} 
Based on the fitted model, we can then estimate the probability of a reaction 
time being below a certain threshold (e.g., 0.1). 
Second, we compare reaction times for athletes who have competed
at additional competitions to the 2022 World Track and Field Championship.  By
comparing reaction times from the same athlete across multiple competitions we 
are able to determine if the 2022 data differed significantly from other 
competitions.
Our investigation into reaction times is important not only because if its
implications for future races, but also because reaction times have
been shown to affect the overall time of the race \citep{delalija2008reaction}.
Thus, faster reaction times lead to faster overall times; which is the goal of
every sprinter who steps onto the track.
%\eds{I recommend moving the rest of this paragraph to Section 2.2 as I don't
%think it is critical for readers to know all the details here.}
%First we can compare the reaction times of athletes who
%competed at the World Track and Field Championships in both 2019 and 2022, and 
%second we can compare how athletes performed at the 2022 championships relative 
%to their national/qualifiers meet. In order to reduce any chances
%of athletes improving reaction time, we can also look at data from qualifying meets.
%Almost every athlete had to qualify by proving they are elite at the national level, 
%usually by coming in at least fourth. Thus, data was compiled on athletes who competed
%at the 2022 World Track and Field Championships on what these athletes also ran 
%at their country's national championship. If there was any argument that athletes
%have improved their reaction time from 2019 to 2022, it should now be considered
%nearly null, as the national competitions took place between June and July 2022 
%and the World Championships were in August. The equipment used to measure reaction
%time cannot be guaranteed to be the same from national to international
%competition, but the time span between meets has been reduced considerably.

@@

This dataset is too small to perform any meaningful statistical analysis, but
the data was expanded to include reaction times for athletes who competed at 
national competitions (many of which were held from May-July of 2022). Once the 
data was collected, each athlete was designated as a cluster and the stage of
competition (national or international) was specified for each competition 
within the cluster (athlete).  \eds{this is where you can put the relevant 
information about the other competitions that was commented out in the 
introduction.}
\eds{Can you show some descriptive statistics for this data?  Total number of 
clusters? Average number of international vs national competitions across 
athletes/clusters?}

>>>>

%4)
The objective to this paper is to analyze the reaction times at the 2022 World 
Track and Field Championships to check for any abnormalities, and we approach
this two different ways.  First we model the data, which is
the reaction times of every non-disqualification since the 1999 World 
Championships, using a gamma linear mixed-effects model with a random effect 
accounting for the venue (or year). 
%\eds{are you using covariates?  Data section
%implies that you are, but Results section does not}
%\of{Cleaned up confusion about covariates, but no none were used in the paper} 
Based on the fitted model, we can then estimate the probability of a reaction 
time being below a certain threshold (e.g., 0.1). 
Second, we compare reaction times for athletes who have competed
at additional competitions to the 2022 World Track and Field Championship.  By
comparing reaction times from the same athlete across multiple competitions we 
are able to determine if the 2022 data differed significantly from other 
competitions.
Our investigation into reaction times is important not only because if its
implications for future races, but also because reaction times have
been shown to affect the overall time of the race \citep{delalija2008reaction}.
Thus, faster reaction times lead to faster overall times; which is the goal of
every sprinter who steps onto the track.

@@

This dataset is too small to perform any meaningful statistical analysis, but
the data was expanded to include reaction times for athletes who competed at 
national competitions (many of which were held from May-July of 2022). Once the 
data was collected, each athlete was designated as a cluster and the stage of
competition (national or international) was specified for each competition 
within the cluster (athlete).  \eds{this is where you can put the relevant 
information about the other competitions that was commented out in the 
introduction.}
\eds{Can you show some descriptive statistics for this data?  Total number of 
clusters? Average number of international vs national competitions across 
athletes/clusters?}
\eds{I recommend moving the rest of this paragraph to Section 2.2 as I don't
think it is critical for readers to know all the details here.}
\of{Is the one below what you're talking about?}
First we can compare the reaction times of athletes who
competed at the World Track and Field Championships in both 2019 and 2022, and 
second we can compare how athletes performed at the 2022 championships relative 
to their national/qualifiers meet. In order to reduce any chances
of athletes improving reaction time, we can also look at data from qualifying meets.
Almost every athlete had to qualify by proving they are elite at the national level, 
usually by coming in at least fourth. Thus, data was compiled on athletes who competed
at the 2022 World Track and Field Championships on what these athletes also ran 
at their country's national championship. If there was any argument that athletes
have improved their reaction time from 2019 to 2022, it should now be considered
nearly null, as the national competitions took place between June and July 2022 
and the World Championships were in August. The equipment used to measure reaction
time cannot be guaranteed to be the same from national to international
competition, but the time span between meets has been reduced considerably.
